\bf{Commonality Analysis for Lattice Boltzmann Systems}

### 2021-10-06 StateOfPractice/DomainMeasurements/LBM-Peter/Commonality-Analysis-LB-Systems.tex
Rearrange domain measurement reports to have more consistent naming and locations

@@

	\begin{tabular}{| p{\colAwidth} | p{\colBwidth}|}		
		\hline
		\bf Description & LBS shall be efficiently easy to use.\\
		\hline
		\bf Related Variability & \vref{varusability}\\
		\hline
		\bf History & Created April 1, 2020\\
		\hline
	\end{tabular}
\end{minipage}\\
\newpage
\section{Variabilities}\label{var_sec}
This section provides a list of characteristics that may vary among family members. As in Section \ref{comm_sec}, the first three subsections on variabilities are organized into the following sublists: Mesh Generation, Input and Output. The final two subsections list variabilities that can be characterized as system constraints and as nonfunctional requirements.

@@

	\begin{tabular}{| p{\colCwidth} | p{\colDwidth}|}		
		\hline
		\bf Description & Various Transport Equations can be used to describe the statistical behaviour of the system\\
		\hline
		\bf Related Commonality & \cref{Boltzmanntransequ}\\
		\hline
		\bf Related Parameter & \pref{partransequ}\\
		\hline
		\bf History & Created April 1, 2020\\
		\hline
	\end{tabular}
\end{minipage}\\
~\newline\\
~\newline
\noindent
\begin{minipage}{\textwidth}
	\renewcommand*{\arraystretch}{1.5}
	\begin{tabular}{| p{\colCwidth} | p{\colDwidth}|}
		\hline
		\bf Item Number&  V\refstepcounter{varnum}\thevarnum\label{numberoffluids} \\
		\hline
	\end{tabular}\\

@@

	\begin{tabular}{| p{\colEwidth} | p{\colFwidth}|}		
		\hline
		\bf Corresponding Variability & \vref{parallel}\\
		\hline
		\bf Range of Parameters & If parallelism is used, commonly OpenMP, OpenCL, CUDA, or MPI are used.\\
		\hline
		\bf Binding Time & Build Time\\
		\hline
	\end{tabular}
\end{minipage}\\
~\newline\\
~\newline
\noindent
\begin{minipage}{\textwidth}
	\renewcommand*{\arraystretch}{1.5}
	\begin{tabular}{| p{\colEwidth} | p{\colFwidth}|}
		\hline
		\bf Item Number& P\refstepcounter{parnum}\theparnum\label{paredf} \\
		\hline
	\end{tabular}\\

>>>>

\noindent\textbf{BGK}: Bhatnagar-Gross-Krook\\

\noindent\textbf{CPU}: central processing unit\\

\noindent\textbf{GPU}: graphics processing unit\\

\noindent\textbf{MRT}: multi-relaxation-time\\

\noindent\textbf{SRT}: single-relaxation-time\\

\noindent\textbf{TRT}: two-relaxation-time\\

@@

	\begin{tabular}{| p{\colAwidth} | p{\colBwidth}|}		
		\hline
		\bf Description & The use of LBS is easy and efficient.\\
		\hline
		\bf Related Variability & \vref{varusability}\\
		\hline
		\bf History & Created April 1, 2020\\
		\hline
	\end{tabular}
\end{minipage}\\
\newpage
\section{Variabilities}\label{var_sec}
This section provides a list of characteristics that may vary among family members. As in Section \ref{comm_sec}, the first three subsections on variabilities are organized into the following sublists: Mesh Generation, Input and Output. The final two subsections list variabilities that can be characterized as system constraints and as nonfunctional requirements.

@@

	\begin{tabular}{| p{\colCwidth} | p{\colDwidth}|}		
		\hline
		\bf Description & Various transport equations can be used to describe the statistical behaviour of the system\\
		\hline
		\bf Related Commonality & \cref{Boltzmanntransequ}\\
		\hline
		\bf Related Parameter & \pref{partransequ}\\
		\hline
		\bf History & Created April 1, 2020\\
		\hline
	\end{tabular}
\end{minipage}\\
~\newline\\
~\newline
\noindent
\begin{minipage}{\textwidth}
	\renewcommand*{\arraystretch}{1.5}
	\begin{tabular}{| p{\colCwidth} | p{\colDwidth}|}
		\hline
		\bf Item Number&  V\refstepcounter{varnum}\thevarnum\label{numberoffluids} \\
		\hline
	\end{tabular}\\

@@

	\begin{tabular}{| p{\colEwidth} | p{\colFwidth}|}		
		\hline
		\bf Corresponding Variability & \vref{parallel}\\
		\hline
		\bf Range of Parameters & OpenMP, OpenCL, CUDA, or MPI are used if LBS is parallel.\\
		\hline
		\bf Binding Time & Build Time\\
		\hline
	\end{tabular}
\end{minipage}\\
~\newline\\
~\newline
\noindent
\begin{minipage}{\textwidth}
	\renewcommand*{\arraystretch}{1.5}
	\begin{tabular}{| p{\colEwidth} | p{\colFwidth}|}
		\hline
		\bf Item Number& P\refstepcounter{parnum}\theparnum\label{paredf} \\
		\hline
	\end{tabular}\\
